%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {BAYKAR Technologies} % Organisation
    {İstanbul, Turkey} % Location
    {October 2024 - December 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Artificial Intelligence and Software Development Department}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {\href{https://tubitak.gov.tr/tr}{\underline{TUBITAK}} (The Scientific and Technological Research Council of Turkey)} % Organisation
    {Kocaeli, Turkey} % Location
    {August 2022 - September 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted research and experiments in image processing, improving algorithm efficiency and applying academic knowledge to develop and test algorithms.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Team Leader} % Job title
    {\href{https://itunomuav.itu.edu.tr/}{\myuline{ITUNOM UAV Team}}} % Organisation
    {Istanbul, Turkey} % Location
    {July 2023 - September 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a 24-person team to 2nd place among 69 teams at SUAS by developing UAV systems (mechanical, software, avionics) and enhanced leadership and project management skills.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Subteam Member} % Job title
    {ITUNOM UAV Team} % Organisation
    {Istanbul, Turkey} % Location
    {September 2022 - September 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed reinforcement and deep learning solutions for UAV dogfighting and object detection, contributing to the team's top finishes at TEKNOFEST and AUVSI SUAS. Implemented optimization algorithms in Gazebo simulation.}
        \item {Enhanced image processing and vision-based localization algorithms, successfully developing image-based control systems.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Subteam Member} % Job title
    {Vefa Aerospace} % Organisation
    {Istanbul, Turkey} % Location
    {November 2021 - August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formulated algorithms for the TEKNOFEST Free Duty UAV Competition, enhancing autonomous drone movement and improving mission completion efficiency by 30\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Creative Designer} % Job title
    {Kampuslu} % Organisation
    {Istanbul, Turkey} % Location
    {July 2021 - January 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided graphic design and video editing services for a startup in exchange for equity.}
        \item {Developed visual content to enhance brand identity and marketing efforts.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {\href{https://www.trtworld.com/}{\underline{TRT World}}} % Organisation
    {Istanbul, Turkey} % Location
    {July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Digital \& Strategy Department}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Member, Instructor \& Team Leader} % Job title
    {TeknoKaihl} % Organisation
    {Istanbul, Turkey} % Location
    {December 2016 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led and conducted training sessions in graphic design, video editing, and directing, along with event organization.}
        \item {Gained extensive experience in both creative and organizational skills through hands-on teaching and leadership.}
      \end{cvitems}
    }

\end{cventries}